---
title: "Actor Analysis"
author: "Derek Wu"
date: "2/18/2020"
output: html_document
---

```{r setup, include=FALSE}
#setwd("./")
source("analysis.R")
knitr::opts_chunk$set(echo = TRUE)
actor_name <- "Brad Pitt"
```

## Brat Pitt Actor Analysis

This is a report with some analysis of trending actors and more in depth analysis of Brad Pitt based on the Movie
Database API. This report analyzes different actors and their work.

## Trending Actors

This is data on trending actors that comes from the week of `r Sys.Date()-7` to `r Sys.Date()`
```{r trending, echo=FALSE}
trending_df <- get_trending_table(key_param)
kable(trending_df)
```

## `r actor_name`


```{r actor analysis, echo=FALSE}
actor_data <- get_actor_data(actor_name)

actor_id <- actor_data[2]
imdb_id <- actor_data[3]
actor_URL <- paste0("https://www.imdb.com/name/", imdb_id)
actor_films <- paste("-", actor_data[5], collapse = "\n")

biography <- actor_data[4]
```

The actor `r actor_name` has the id of `r actor_id`. `r actor_name`'s IMDB page can be found [here](`r actor_URL`). `r biography`. `r actor_name` is known for his work in `r actor_films`.

### `r actor_name` Film Popularity as Director vs Executive Director

```{r brad pitt analysis, echo=FALSE}
result <- analyze_actor(key_param)
roles <- result[[1]][1]
pop <- result[[1]][2]
vote <- result[[1]][3]
```

When `r actor_name` works on a film as the `r roles[[1]][1]`, the movie has an average popularity of `r pop[[1]][1]` and average rating of `r vote[[1]][1]`. However, when `r actor_name` works on a movie as the `r roles[[1]][2]`, the movie has an average popularity of `r pop[[1]][2]` and an average rating of `r vote[[1]][2]`. This difference of `r pop[[1]][1] - pop[[1]][2]` popularity and `r vote[[1]][1] - vote[[1]][2]` may be caused by the different amount of experience and help `r actor_name` has in each of these positions.

The raw data used in this calculation is presented below.
```{r rawdata, echo=FALSE}
raw <- result[[2]]
kable(raw)
```